---
title: "**listgen** usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows how to use the `listgen` package to generate a permutted list of students.



```{r, echo = FALSE}
# whether to evaluate the code
EVAL = FALSE
```


## Installation

You have to install the `listgen` package from GitHub. To do this, you need the `devtools` package. If you don't have it, install it with:

```{r install, eval = FALSE}
devtools::install_github("mkvasnicka/listgen")
```



## Get list of students from IS

Let's say that the list of students is available in the Information system of the Masaryk University. Then we can download it with **MUIS** package.  Let's further say we want the get students of two joined courses, BPE_MIE1 and MPE_MIVS. All students of MPE_MIVS attend the seminary group\ 26 in BPE_MIE. Thus we can get the list (or rather *tibble*) of students with the following code:

```{r, eval = EVAL}
library(MUIS)

micro <- credentials(
  key = "Z6o4VCwTOPPYGWI9",
  faculty = 1456,
  course = "BPE_MIE1"
)
mivs <- credentials(
  key = "T_EVbceQ0fdFaulj",
  faculty = 1456,
  course = "MPE_MIVS"
)

students <- bind_rows(
  get_seminar_students(micro),
  get_seminar_students(mivs) |> mutate(seminar = "26")
)
```



## **listgen** usage

Load the package:

```{r setup, eval = EVAL}
library(listgen)
```

For reproducibility, set the seed. Then generate the list of students:

```{r, eval = EVAL}
set.seed(1234)
listgen(students)
```
