---
title: "**listgen** usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows how to use the `listgen` package to generate a permuted list of students.



```{r, echo = FALSE}
# whether to evaluate the code
EVAL = FALSE
```


## Installation

You have to install the `listgen` package from GitHub. To do this, you need the `devtools` package. If you don't have it, install it with:

```{r install, eval = FALSE}
devtools::install_github("mkvasnicka/listgen", build_vignettes = TRUE)
```

Notes:

- the package needs **pdflatex** to be installed on your system
- as it creates LaTeX files and compiles it, the code is not run in the vignette.



## Basic **listgen** usage

First, load the package:

```{r setup, eval = EVAL}
library(listgen)
```

Second, you need a tibble of all students. The tibble must contain the following columns:

- `course` - course code
- `seminar` - seminar group code
- `uco` - student's unique ID
- `last_name` - student's last name
- `first_name` - student's first name

Here is an example of such tibble:

```{r}
students <- tibble::tribble(
  ~course, ~seminar, ~uco, ~last_name, ~first_name,
  "BPE_AAA", "01", 123456, "Aloha", "Adam",
  "BPE_AAA", "01", 234567, "Brown", "Betty",
  "BPE_AAA", "01", 345678, "Cook", "Charlie",
  "BPE_AAA", "01", 456789, "Delacroix", "Diana"
)
students
```

Now, you can generate the list of students with the `listgen` function.
However, for reproducibility, it is a good idea to set the seed first. Then generate the list of students:

```{r, eval = EVAL}
set.seed(1234)
listgen(students, max_lag = 2)
```

In this case, the list of students is generated in R `tempdir()` and is called `listgen.pdf`. You can set the folder and name by the corresponding arguments. If you use the package on a Linux machine with installed `evince`, you can instead ask it to open the file for you:

```{r, eval = EVAL}
listgen(students, max_lag = 2, open = TRUE)
``` 

For a small groups of students, such as presented in the example above, you should set the `max_lag` parameter to one:

```{r, eval = EVAL}
listgen(students, max_lag = 1, open = TRUE)
```

Other parameters are described in the documentation of the `listgen` function.


## Get list of students from IS

Let's say that the list of students is available in the Information system of the Masaryk University. Then we can download it with **MUIS** package.  Let's further say we want the get students of two joined courses, BPE_MIE1 and MPE_MIVS. All students of MPE_MIVS attend the seminary group\ 26 in BPE_MIE. Thus we can get the list (or rather *tibble*) of students with the following code:

```{r, eval = EVAL}
library(MUIS)
library(dplyr)

micro <- credentials(
  key = "Z6o4VCwTOPPYGWI9",
  faculty = 1456,
  course = "BPE_MIE1"
)
mivs <- credentials(
  key = "T_EVbceQ0fdFaulj",
  faculty = 1456,
  course = "MPE_MIVS"
)

students <- bind_rows(
  get_seminar_students(micro),
  get_seminar_students(mivs) |> mutate(seminar = "26")
)

listgen(students, open = TRUE)
```
